\documentclass[12pt]{amsart}

\usepackage[left=1.4cm, right=1.4cm, bottom=4cm]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\setlength\parskip{5pt}
\renewcommand{\baselinestretch}{1} 
\pagestyle{empty}


\begin{document}
\begin{center}{\large{\bf Marco Badran}}\end{center}
\noindent\rule{\textwidth}{.8pt}
\medskip\bigskip

\noindent{\bf General informations}
\begin{itemize}
	\item {work address}: {ETH Z\"urich, R\"amistrasse 101, 8006 Z\"urich, HG FO 28.7}
	\item {email}: marco.badran@math.ethz.ch
	\item {research interest}: Geometric analysis, minimal surfaces (local and nonlocal), harmonic maps (classical and fractional).
	\item {website}:  {\color{blue} \url{https://marco-badran.github.io}}
\end{itemize}

\bigskip\medskip
\noindent{\bf Positions}
\begin{itemize}
	\item {Sep. 2023.} Postdoctoral position at ETH Z\"urich with Prof. Joaquim Serra.
\end{itemize}

\bigskip\medskip
\noindent{\bf Education}
\begin{itemize}
	\item {2019 -- 2023}\\ 
		Ph.D. in Mathematics at University of Bath, UK. Supervisor: Prof. Manuel del Pino.\\
		Thesis: \emph{Concentrating solutions in the magnetic Ginzburg--Landau model.}
		Defended on 28th April 2023.
	
	\medskip
	
	\item {2017 -- 2019}\\  Master in Mathematics at Universit\`a degli Studi Milano, IT. Supervisor: Prof. Bernhard Ruf. \\
		Thesis: \emph{The Allen--Cahn equation: a conjecture by De Giorgi.}
	
	\medskip
	
	\item {2014 -- 2017}\\  Bachelor in Mathematics at Universit\`a degli Studi Milano, IT.
\end{itemize}

\bigskip\medskip
\noindent{\bf Preprints and articles}
\begin{enumerate}
	\item with M. del Pino:
		\emph{Entire solutions to 4-dimensional Ginzburg--Landau equations and codimension 2 minimal submanifolds.} (Adv. Math.)
	\item with M. del Pino: \emph{Solutions of the Ginzburg--Landau equations concentrating on codimension-2 minimal submanifolds.} Preprint (J. London Math. Soc)
\end{enumerate}

\bigskip\medskip
\noindent{\bf Invited speaker - seminars}
\begin{itemize}
	\item {Dec.\ 20, 2022} -- Analysis seminar -- UniMi, Milano
	\item {Jan.\ 11, 2023} -- Geometry seminar -- UCL, London
	\item {Jan.\ 20, 2023} -- Analysis seminar -- UAM/ICMAT, Madrid 
	\item {Feb.\ 16, 2023} -- Analysis seminar -- University of Bath, Bath
	\item {Oct.\ 6, 2023} -- Young researchers in PDEs -- UAM/ICMAT Madrid
	\item {Feb.\ 7, 2024} -- Analysis \& PDE seminar -- NUS Singapore
\end{itemize}

\bigskip\medskip
\noindent{\bf Visiting periods}
\begin{itemize}
	\item {May 31 - Jun.\ 16, 2023} at ETH Z\"urich.
	\item {Feb.\ 2 - Feb.\ 12, 2024} at NUS Singapore
\end{itemize}

\bigskip\medskip
\noindent{\bf Attended conferences/workshops}
\begin{itemize}
	\item {Jul.\ 2019}. XI Workshop in Nonlinear	 Differential Equations -- Varese, Italy. 
	\item {Dec.\ 2022}. Workshop on Geometric PDEs -- Warwick, UK. 
	\item {Apr.\ 2023}. British Mathematical Colloquium -- Bath, UK.
	\item {Jun.\ 2023}. Regularity Theory for Free Boundary and Geometric Variational Problems III -- Levico Terme, Italy.
	\item {Sep.\ 2023}. Conference in honour of Luigi Ambrosio's 60th birthday -- ETH Z\"urich
	\item {Sep.\ 2023}. Young researchers in PDEs -- UAM/ICMAT Madrid
	\item {Jan.\ 2024}. New Trends in Nonlinear PDEs, Physics and Geometry -- IMAG Granada
	\item 
\end{itemize}

\bigskip\medskip
\noindent{\bf Teaching}
\begin{itemize}
	\item 2019 -- 2023. Graduate Teaching Assistant at Univeristy of Bath. 
	\item Spring 2024. Organiser for Analysis IV, ETH Z\"urich.
\end{itemize}
%% make precise estimate: like 2hr per week..

\bigskip\medskip
\noindent{\bf Referee for}
\begin{itemize}
	\item Advances in Differential Equations.
\end{itemize}

\bigskip\medskip
\noindent{\bf Languages}
\begin{itemize}
	\item Italian (native)
	\item English (fluent)
	\item Spanish (good) 
\end{itemize}

\end{document}
