\documentclass[a4paper,11pt]{article}

% Font and Encoding
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern} % Default LaTeX modern font

% Page Layout
\usepackage{geometry}
\geometry{left=1in,right=1in,top=1in,bottom=1in}

% Optional: No paragraph indentation and add spacing between paragraphs
\usepackage{parskip}

% Links
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue
}

% Elegant Section Formatting
\usepackage{titlesec}
\titleformat{\section}{\normalfont\large\scshape}{}{0pt}{}[\titlerule]

% No page numbers
\pagestyle{empty}

\begin{document}

% Name and Contact Information
\begin{center}
    {\Large \textsc{Marco Badran}} \\ % Smaller name size
    \vspace{2mm}
    \small Postdoc at ETH Z\"urich \\
    \vspace{2mm}
    \href{mailto:marco.badran@math.ethz.ch}{email} | \href{https://marco-badran.github.io/marco-badran/}{website} 
\end{center}

\vspace{10mm}

% Employment
\section*{Employment}
\noindent
\textbf{Postdoc at ETH Z\"urich} \\
2023 -- ongoing \\
Mentor: Prof.\ Joaquim Serra.
\vspace{5mm}

% Education Section
\section*{Education}
\noindent
\textbf{Ph.D. in Mathematics} \\
University of Bath, 2019 -- 2023 \\
Thesis Title: \textit{Concentrating solutions in the magnetic Ginzburg--Landau model.} \\
Supervisor: Prof. Manuel del Pino.

\vspace{3mm}

\textbf{Master in Mathematics} \\
Università statale di Milano, 2017 -- 2019 \\
Thesis Title: \textit{The Allen--Cahn equation: a conjecture by De Giorgi.} \\
Supervisor: Prof. Bernhard Ruf.

\vspace{3mm}

\textbf{Bachelor in Mathematics} \\
Università statale di Milano, 2014 -- 2017 

\vspace{5mm}

% Basic Research Interests Section
\section*{Preprints and publications}
\noindent
\begin{itemize}
	\item \emph{Stationary $p$-harmonic maps approaching planar singular harmonic maps to the circle.} (with J. Van Schaftingen) {\bf arXiv}
	\item \emph{Harmonic maps to the circle with higher dimensional singular set.} {\bf arXiv}
	\item \emph{Solutions of the Ginzburg--Landau equations concentrating on codimension-2 minimal submanifolds.} (with M. del Pino.) {\bf J. London Math. Soc.}
	\item \emph{Entire solutions to 4-dimensional Ginzburg--Landau equations and codimension 2 minimal submanifolds.} (with M. del Pino.) {\bf Adv. Math.}
\end{itemize}

\vspace{5mm}

\section*{Invited speaker - seminars}
\noindent
\begin{itemize}
	\item Analysis seminar, UniMi Milano ({12.22})
	\item Geometry seminar, UCL London ({01.23})
	\item Analysis seminar,  UAM/ICMAT Madrid (01.23)
	\item Analysis seminar, University of Bath (02.23)
	\item Young researchers in PDEs, UAM/ICMAT Madrid (10.23)
	\item Analysis \& PDE seminar, NUS Singapore (02.24)
	\item Analysis Seminar, ETH Z\"urich (02.25)
	\item Analysis Seminar, SNS Pisa (03.25)
	\item PDE Seminar, Cambridge (05.25)
\end{itemize}
\vspace{5mm}

%Teaching
\section*{Teaching}
\noindent
\begin{itemize}
	\item Graduate Teaching Assistant at University of Bath (several courses, 2019 -- 2023)
	\item Organiser for \emph{Analysis IV}, D-MATH ETHZ. (Spring 2024)
	\item Lecturer for \emph{Nonlinear Analysis and Perturbation Methods}, D-MATH ETHZ. (Fall 2024)
	\item Organiser for \emph{Analysis I}, D-INFK ETHZ (Spring 2025)
	\item Organiser for \emph{Partial Differential Equations}, D-MATH ETHZ (Spring 2025)
\end{itemize}
\vspace{5mm}

%Refereeing service
\section*{Other activities}
\noindent
\textbf{Referee for:} Adv.\ Differential Equations, Ars Inven.\ Analytica, Proc.\ London Math.\ Soc., Discrete Contin.\ Dyn.\ Sys., Journal of Differential Equations\\
 
\noindent
\textbf{Supervision:} 
\begin{itemize}
	\item Matteo Gatti (Bachelor thesis -- ETH Z\"urich, 2025)
	\item Lennard Trautmann (Semester paper -- ETH Z\"urich, 2025)
	\item Luana Jost (Semester paper -- ETH Z\"urich, 2025)
	\item Derk Steffens (Reading Course -- ETH Z\"urich)
\end{itemize}
\vspace{5mm}

\end{document}
